\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
fix: remove repetitive paragraph

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, innovation is also needed to incorporate this information into the systems. For example, even \PaperQATwo could not outperform the \gls{llm} it is using for directing the tools, even though the agent has access to literature evidence.
This suggests we might need to not only focus on building chemistry-specific retrieval datasets since current systems fail to retrieve the relevant systems and should be coupled with more domain-specific databases. However, the observation that our ReAct agents were too fragile to answer questions for which they had custom-made tools available correctly suggests that we also must invest in building more robust agent frameworks.

@@

As commented above, \PaperQATwo was outperformed by the \gls{llm} powering it. Similarly, \ClaudeThreeFiveSonnet only slightly improved the results when equipped with some specific tools, while \GPTFourO performance decreased in this same tool environment (see \Cref{sec:react-environment} for further discussion about the ReAct environment). Therefore, a robust chemical agent framework optimized to solve general chemical problems instead of focusing on bibliographic search or lab work can be useful in the future.

>>>>

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, innovation is also needed to incorporate this information into the systems. For example, even \PaperQATwo could not outperform the \gls{llm} it is using for directing the tools, even though the agent has access to literature evidence.
This suggests we might need to not only focus on building chemistry-specific retrieval datasets since current systems fail to retrieve the relevant systems and should be coupled with more domain-specific databases. However, the observation that our ReAct agents were too fragile to answer questions for which they had custom-made tools available correctly suggests that we also must invest in building more robust agent frameworks (see \Cref{sec:react-environment} for further discussion about the ReAct environment).

@@
